Semantic Photographic Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-10-16 cvpr2018.tex
add architecture" "

We have validated our proposed method on three datasets, i.e. CUB birds, Oxford-102 flowers, and large-scale COCO datasets. Extensive experimental results demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts.

@@

Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks like image classification \cite{lee2015deeply} and edge detection \cite{xie2015holistically}. DSN \cite{lee2015deeply} introduces deep supervision in hierarchical convolutional layers to increase the discriminativenss of feature representations. In aspect of unsupervised learning, Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images conditioned on noise and images from last pyramid, and gradually increase image resolution. StackGAN also shares similar strategy with LAPGAN to increase output resolution. Different from these methods,

deep supervision

@@

@@

\subsection{Network Architecture}

>>>>

We have validated our proposed method on three datasets, i.e. CUB birds \cite{}, Oxford-102 flowers \cite{}, and large-scale COCO datasets \cite{}. Extensive experimental results demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts.

@@

In term of high resolution image synthesis, cascade networks plays an important role.
Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and output from last level of the pyramid, to push up output resolution through by-stage refinement. StackGAN also shares similar strategy with LAPGAN. Following this Chen \etal \cite{chen2017photographic} present a cascaded refinement networks to synthesis high-resolution scene from semantic maps.

Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks like image classification \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified}. DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations. Inspired by DSN, our method that has accompanying deeply-nested adversarial supervision can be viewed as a way to enhance effective feature representation, so as to support end high resolution outputs.

@@

\subsection{Architecture}
Our proposed network, composed by a generator and a discriminator, is symmetric as well as extensile. We introduce the details as well as motivations.

The generator is simpled composed by three kinds of modules, termed as $K$-repeat residual blocks, stretching layers, and linear composition layers.
A single residual block in the $K$-repeat residual block contains two convolutional layers (with pre-activated batch normalization (BN) \cite{} and ReLU following \cite{he2016identity}). The stretching  layer serves to reduce feature map size and dimension. It simply contains an scale-$2$ nearest up-sampling followed by a convolutional layer with BN+ReLU.  And the linear composition layer is a convolutional layer followed by a Tanh to linearly represent RGB images.
Starting from a $1024{\times}4{\times}4$ embeddings replicated by a $1024$-d text embedding, the generator simples use $M$ $K$-repeat residual block connected by $M-1$ in-between stretching layers until the feature maps reach to the targeting resolution. We use $K{=}2$ in our method. So for $256{\times}256$ targeting resolution , there are $M{=}6$ $2$-repeat residual blocks and $5$ stretching layers. With a predefined side-output scales $\{S_i\}$, we apply the compositional layers at those scales to generate image at different scales and as inputs of discriminators.

@@
